---
title: "NEUORAL NETWORKS FOR APPROXIMATION"
output:
  word_document: default
  html_notebook: default
  html_document: default
---

# Download the data and libraries
```{r}
library(knitr)
library (psych)
library(dplyr)
library(ggplot2)

f <- read.csv2('flats.csv', header = TRUE, encoding = 'UNICOD')
describe(f)
```
## Factors as numeric
```{r}
f$location <- as.numeric(as.factor(f$location))
f$condition <- as.numeric(as.factor(f$condition))
f$type <- as.numeric(as.factor(f$type))
```

## Ejections (outside the three sigma)
```{r}
f_ej <- f
f_ej$price <- ifelse(f$price < mean(f$price)+sd(f$price)*3, f$price,mean(f$price)+sd(f$price)*3)
describe(f_ej$price)
f <- f_ej
```

## Missing data, fill n/a with average 
```{r}
f_fill <- f
f_fill$rooms <- ifelse(is.na(f$rooms),round(mean(f$rooms,na.rm = TRUE)),f$rooms)
f_fill$type <- ifelse(is.na(f$type),round(mean(f$type,na.rm = TRUE)),f$type)
f <- f_fill
```

## Splitting the scaled dataset into the TRAIN set and TEST set
```{r}
set.seed(123)
library(caTools)
split = sample.split(f$price, SplitRatio = 0.8)
f_train = subset(f, split == TRUE)
f_test = subset(f, split == FALSE)
```

## Features Scaling
```{r}
f_train_sc <- as.data.frame(scale(f_train))
f_test_sc <- as.data.frame(scale(f_test))
head (f_train_sc)
```
# Fitting the NN
```{r results='hide'}
library(nnet)
ff_ap <- nnet(price ~ rooms + location + condition + m2, f_train_sc, linout = TRUE ,size = 4, maxit = 10000)
library(graphics)
source(file = 'plot.nnet.R')
plot.nnet(ff_ap)
```

## Prediction
```{r}
p_y_train <- predict(ff_ap, f_train_sc)
p_y_test <- predict(ff_ap, f_test_sc)
```

## Invert the effect of the scale function
```{r}
sc_y_train <- scale(f_train$price)
y_train <- DMwR::unscale(p_y_train, sc_y_train)
sc_y_test <- scale(f_test$price)
y_test <- DMwR::unscale(p_y_test, sc_y_test)
```

## MSE
```{r}
train_mse <- sum((f_train$price-y_train)^2)/length(f_train$price)
test_mse <- sum((f_test$price-y_test)^2)/length(f_test$price)

train_mse
test_mse
```

## Visualising
```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(f_train$m2, f_train$price),colour = 'red') +
  geom_point(aes(f_test$m2, f_test$price),colour = 'dark green') +
  geom_point(aes(f_test$m2, y_test),colour = 'blue', size = 3, alpha=0.5) +
  ggtitle('Price vs m2') +
  xlab('m2') +
  ylab('price')
```

# Fit NN-2 
```{r  results='hide'}
library(neuralnet)

# fit neural network
nn = neuralnet(price ~ rooms + location + condition + m2, f_train_sc, hidden = 3, linear.output = T)

# plot neural network
plot(nn)
```

```{r}
p_y_train_nn <- predict(nn, f_train_sc)
p_y_test_nn <- predict(nn, f_test_sc)
```

## Invert the effect of the scale function
```{r}
y_train_nn <- DMwR::unscale(p_y_train_nn, sc_y_train)
y_test_nn <- DMwR::unscale(p_y_test_nn, sc_y_test)
```

## MSE
```{r}
train_mse_nn <- sum((f_train$price-y_train_nn)^2)/length(f_train$price)
test_mse_nn <- sum((f_test$price-y_test_nn)^2)/length(f_test$price)

train_mse_nn
test_mse_nn
```
## Visualising
```{r}
library(ggplot2)
ggplot() +
  geom_point(aes(f_train$m2, f_train$price),colour = 'red') +
  geom_point(aes(f_test$m2, f_test$price),colour = 'dark green') +
  geom_point(aes(f_test$m2, y_test),colour = 'blue', size = 3, alpha=0.5) +
  ggtitle('Price vs m2') +
  xlab('m2') +
  ylab('price')
```

# Saving results
```{r}
fit <- read.csv2('flats_fit.csv', header = TRUE, encoding = 'UNICOD')
fit$p_nn <- y_test_nn
head(fit)
write.csv2(fit[-1], file = "flats_fit.csv")
```

## Compare models
```{r}
g_sr <- ggplot(fit, aes(x=f_test.price, y=p_sr)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Linear Regression", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none")

g_mr <- ggplot(fit, aes(x=f_test.price, y=p_mr)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Multiple Regression", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none")

g_pr <- ggplot(fit, aes(x=f_test.price, y=p_pr)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Polynomial Regression", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none") 

g_dt <- ggplot(fit, aes(x=f_test.price, y=p_dt)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Regression Tree", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none")

g_rf <- ggplot(fit, aes(x=f_test.price, y=p_rf)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Random Forest", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none")

g_nn <- ggplot(fit, aes(x=f_test.price, y=p_nn)) + 
  geom_abline(intercept=0, slope=1) +
  geom_point(color = 'red', alpha=0.5) + labs(title="Neural Network", x="Real Price", y="Predicted Price") + 
  theme(plot.title=element_text(size=10), axis.title.x=element_text(size=7), axis.title.y=element_text(size=7), axis.text.x=element_text(size=5), axis.text.y=element_text(size=5)) + theme(legend.position="none")

gridExtra::grid.arrange(g_sr,g_mr,g_pr,g_dt,g_rf,g_nn,ncol=2)
```