---
title: "Feature Extraction - PCA"
output:
  word_document: default
  html_notebook: default
  html_document: default
---

# Download the data
```{r}
set.seed(123)
#setwd('D:/ML')
f <- read.csv('bank.csv', header = TRUE, encoding = 'UNICOD')
f <- f[-1]
```

## Features Encoding & Scaling
```{r}
f$region = as.numeric(factor(f$region, levels = c('TOWN', 'INNER_CITY',
           'sUBURBAN','RURAL'),labels = c(1, 2, 3, 4)))
f$sex = as.numeric(factor(f$sex,levels = c('FEMALE', 'MALE'),
                                labels = c(1, 2)))
f$married = as.numeric(f$married)
f$car = as.numeric(f$car)
f$mortgage = as.numeric(f$mortgage)
f$delays = as.numeric(f$delays)-1
f[-9] <- as.data.frame(scale(f[-9]))
```

## Delete N/A
```{r}
f <- tidyr::drop_na(f)
cat('there are',nrow(f),'rows in the f')
```

## Splitting the dataset into the TRAIN set and TEST set
```{r}
set.seed(123)
library(caTools)
split = sample.split(f$delays, SplitRatio = 2/3)
f_train = subset(f, split == TRUE)
f_test = subset(f, split == FALSE)
```

# Applying PCA
```{r}
# install.packages('caret')
library(caret)
# install.packages('e1071')
library(e1071)
pca = preProcess(x = f_train[-9], method = 'pca', pcaComp = 2)
f_train_pca = predict(pca, f_train)
f_train_pca = f_train_pca[c(2, 3, 1)]
f_test_pca = predict(pca, f_test)
f_test_pca = f_test_pca[c(2, 3, 1)]
```

# Fitting SVM to the PCA-Training set
```{r}
# install.packages('e1071')
library(e1071)
classifier = svm(formula = delays ~ .,
                 data = f_train_pca,
                 type = 'C-classification',
                 kernel = 'linear')
```

## Predicting the Test set results
```{r}
y_pred = predict(classifier, newdata = f_test_pca[-3])
```

## Making the Confusion Matrix
```{r}
cm = table(f_test_pca[, 3], y_pred)
print(cm)
```

## Visualising the Test set results
```{r}
library(ElemStatLearn)
set = f_test_pca
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('PC1', 'PC2')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3], main = 'SVM (Test set)',
     xlab = 'PC1', ylab = 'PC2',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 2, 'deepskyblue', ifelse(y_grid == 1, 'springgreen3', 'tomato')))
points(set, pch = 21, bg = ifelse(set[, 3] == 2, 'blue3', ifelse(set[, 3] == 1, 'green4', 'red3')))
```

# Applying Kernel PCA
```{r}
# install.packages('kernlab')
library(kernlab)
kpca = kpca(~., data = f_train[-9], kernel = 'rbfdot', features = 2)
f_train_kpca = as.data.frame(predict(kpca, f_train))
f_train_kpca$delays = f_train$delays
f_test_kpca = as.data.frame(predict(kpca, f_test))
f_test_kpca$delays = f_test$delays
```

# Fitting SVM to the KPCA-Training set
```{r}
# install.packages('e1071')
library(e1071)
classifier = svm(formula = delays ~ .,
                 data = f_train_kpca,
                 type = 'C-classification',
                 kernel = 'linear')
```

## Predicting the Test set results
```{r}
y_pred = predict(classifier, newdata = f_test_kpca[-3])
```

## Making the Confusion Matrix
```{r}
cm = table(f_test_kpca[, 3], y_pred)
print(cm)
```

## Visualising the Test set results
```{r}
library(ElemStatLearn)
set = f_test_kpca
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('V1', 'V2')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3], main = 'SVM (Test set)',
     xlab = 'PC1', ylab = 'PC2',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 2, 'deepskyblue', ifelse(y_grid == 1, 'springgreen3', 'tomato')))
points(set, pch = 21, bg = ifelse(set[, 3] == 2, 'blue3', ifelse(set[, 3] == 1, 'green4', 'red3')))
```